Hydras \& Co.

### 2022-05-19 doc/epsilon0-chapter.tex
Update doc/epsilon0-chapter.tex
Co-authored-by: Karl Palmskog <palmskog@gmail.com>

\paragraph*{\gaiasign}
\index{gaiabridge}{Type of well formed ordinal terms below $\epsilon_0$}
 Our library~\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge} defines also a type \texttt{E0} (which doesn't exist in \gaia-\texttt{ssete9}).

>>>>

\paragraph*{\gaiasign}
\index{gaiabridge}{Type of well formed ordinal terms below $\epsilon_0$}
 Our library~\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge} also defines a type \texttt{E0} (which doesn't exist in \gaia-\texttt{ssete9}).
